Comparative Evaluation of Spark and Flink Stream Processing

### 2017-02-19 paper/paper.tex
added apache kafka

Apache Flink is an open source project that provide large-scale, distributed stream processing platform, while the batch processing treated as special case of streaming (as finite data stream) \cite{flink}.
It offers programming API in Java, Scala. Its stack includes the core DataStream and DataSet APIs with additional libraries such as Complex event processing for Flink (FlinkCEP), Machine Learning for Flink (FlinkML), and Flink Graph API (Gelly).

@@

@@

>>>>

Apache Flink is an open source project that provide large-scale, distributed stream processing platform, while the batch processing treated as special case of streaming applications \cite{flink}.
It offers programming API in Java, Scala. Its stack includes the core DataStream and DataSet APIs with additional libraries such as Complex event processing for Flink (FlinkCEP), Machine Learning for Flink (FlinkML), and Flink Graph API (Gelly).

@@

\subsection{Apache Kafka}
Apache Kafka is scalable, fault-tolerant distributed publish/subscribe streaming framework \cite{kafka}.
It manges the stream records in different categorizes (i.e., topics) that portioned and distributed over the servers in the Kafka cluster. It allows the data producers to publish stream of records to certain Kafka topic. While the consumer applications can subscribe to one or more topic to read the data stream.

@@

\bibitem[5]{kafka} 
Apache Kafka. Available: https://kafka.apache.org/ [Accessed February 2017].
